The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
clarify original+modal lc

Each modal landcover, and the original are sampled and separate network layers constructed for each. **[QW: NOT SURE WHAT THIS MEANS]**

>>>>

For each landcover (the original resolution and modal resampled resolutions), seasonal network layers are combined in a multilayer network
<!-- Each modal landcover, and the original are sampled and separate network layers constructed for each. **[QW: NOT SURE WHAT THIS MEANS]** -->
